---
title: "COVID-19 in Georgia"
author: "Matthew Lovelace"
output: 
  flexdashboard::flex_dashboard:
    social: menu
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(lubridate)
library(ggplot2)
library(glue)
library(plotly)
```

```{r load-and-prep-data, include=FALSE}

## current pop. total ##

# source: U.S. Census Bureau

pop_us <- readxl::read_excel("data/orig/nst-est2019-01.xlsx", 
    skip = 3) %>% 
  rename(state = `...1`,
         pop_est = `2019`) %>% 
  select(state, pop_est) %>% 
  filter(str_detect(state, "[.]") & !is.na(pop_est)) %>% 
  mutate(state = str_replace(state, "[.]", ""))

states <- data.frame(
  state = state.name,
  st = state.abb
) %>% 
  mutate_at(vars(state, st),
            list(~ as.character(.)))

pop_us <- pop_us %>% 
  full_join(states,
            by = "state") %>% 
  mutate(st = if_else(state == 'District of Columbia', 'DC', st))




## daily U.S. covid-19 data ##

# source: COVID Tracking Project

# make data/orig & data/prep folders
for (i in c('orig', 'prep')) {
  if (dir.exists(here::here('data', i)) == FALSE) {
    dir.create(here::here('data', i), recursive = TRUE)
  }
}

# if no dataset already stored for today and it is after 5pm EST/EDT,
# download the lastest COVID Tracking 4pm Daily dataset and load that.
# if the data for today is already there, load that.
# if the data is not there for today and it is before 5pm EST/EDT, check
# if yesterday's data is already downloaded. If so, load that.
# If not, download it and load that.


if (
  file.exists(here::here('data', 'orig', paste0('cov-us-4pm-daily_', today('EST5EDT'), '.csv'))) == FALSE & hour(now("EST5EDT")) >= 17
) {
  
  df <- read.csv('https://covidtracking.com/api/v1/states/daily.csv')
  
  write.csv(df,
            here::here('data', 'orig', paste0('cov-us-4pm-daily_', today('EST5EDT'), '.csv')))
  
  saveRDS(df,
          here::here('data', 'prep', paste0('cov-us-4pm-daily_', today('EST5EDT'), '.rds')))
  
} else if (
  file.exists(here::here('data', 'prep', paste0('cov-us-4pm-daily_', today('EST5EDT'), '.rds'))) == TRUE
) {
  
  df <- readRDS(here::here('data', 'prep', paste0('cov-us-4pm-daily_', today('EST5EDT'), '.rds')))
  
} else if (
  file.exists(here::here('data', 'orig', paste0('cov-us-4pm-daily_', today('EST5EDT') - 1, '.csv'))) == FALSE
) {
  
  df <- read.csv('http://covidtracking.com/api/states/daily.csv')
  
  write.csv(df,
            here::here('data', 'orig', paste0('cov-us-4pm-daily_', today('EST5EDT') - 1, '.csv')))
  
  saveRDS(df,
          here::here('data', 'prep', paste0('cov-us-4pm-daily_', today('EST5EDT') - 1, '.rds')))
} else if (
  file.exists(here::here('data', 'prep', paste0('cov-us-4pm-daily_', today('EST5EDT') - 1, '.rds'))) == TRUE
) {
  
  df <- readRDS(here::here('data', 'prep', paste0('cov-us-4pm-daily_', today('EST5EDT') - 1, '.rds')))
  
} 

cov_us_4pm_daily <- df
rm(df)

cov_us <- cov_us_4pm_daily %>% 
  rename_all(list(~ str_to_lower(.))) %>% 
  rename(dt = date,
         st = state,
         pos = positive,
         neg = negative,
         hosp = hospitalized,
         deaths = death) %>% 
  select(-totaltestresults) %>% 
  mutate(tests = pos + neg) %>% 
  mutate(dt = ymd(as.character(dt))) %>%
  mutate(deaths = if_else(is.na(deaths), 0, as.double(deaths)))



## calculate tests per million ##

cov_us <- cov_us %>% 
  mutate(st = as.character(st)) %>% 
  #select(st, dt, tests) %>% 
  full_join(pop_us,
            by = 'st') %>% 
  ## drops territories like American Samoa ##
  filter(!is.na(state)) %>% 
  ## calc tests per million ##
  mutate(tests_per_million = round(tests*1000000/pop_est))


## positive test rate ##
cov_us <- cov_us %>% 
  mutate(pct_pos = pos/(tests)*100)



## days since 100th case ##

cov_us <- cov_us %>% 
  arrange(dt) %>% 
  mutate(at_least_100 = pos >= 100) %>% 
  group_by(st, at_least_100) %>% 
  mutate(days_since_100 = if_else(at_least_100 == TRUE, row_number(), NA_integer_)) %>%
  ungroup()


## new cases, tests, deaths ##
cov_us <- cov_us %>% 
  arrange(dt) %>% 
  group_by(st) %>% 
  mutate(new_cases = if_else(row_number() == 1,
                             pos,
                             pos - lag(pos)),
         new_deaths = if_else(row_number() == 1,
                              deaths,
                              deaths - lag(deaths)),
         new_tests = if_else(row_number() == 1,
                             tests,
                             tests - lag(tests))) %>% 
  ungroup() %>% 
  mutate_at(vars(tests, pos, neg, deaths, new_cases, new_deaths, new_tests),
            list(~ as.numeric(.)))
  
cov_us <- cov_us %>% 
  select(dt, days_since_100, st, pop_est,
         pos, neg, tests, tests_per_million, pct_pos,
         hosp, deaths,
         new_tests, new_cases, new_deaths)



## 7-day rolling avgs ##

for (var in c('tests', 'tests_per_million', 'pos', 'pct_pos', 'new_tests', 'new_cases', 'new_deaths', 'hosp', 'deaths')) {
  for (i in 1:6) {
    cov_us <- cov_us %>% 
      arrange(st, dt) %>% 
      group_by(st) %>% 
      mutate(!! paste0(var, '_lag_', i) := lag(get(var), i)) %>% 
      ungroup()
  }
}

df <- cov_us %>% 
  select(st, dt, tests, tests_per_million, pos, pct_pos, new_cases, new_tests, new_deaths, hosp, deaths, contains('_lag_')) %>% 
  rename_at(vars(tests, tests_per_million, pos, pct_pos, new_cases, new_tests, new_deaths, hosp, deaths),
            list(~ paste0(., "_lag_0"))) %>% 
  pivot_longer(cols = contains("_lag_"),
               names_to = "var",
               values_to = "val") %>% 
  arrange(st, dt, var) %>% 
  mutate(var = str_sub(var, end = -7)) %>% 
  group_by(st, dt, var) %>% 
  mutate(`_7dra` = mean(val, na.rm = FALSE)) %>% 
  ungroup() %>% 
  distinct(st, dt, var, .keep_all = TRUE) %>% 
  select(st, dt, var, `_7dra`) %>% 
  pivot_wider(names_from = var,
              values_from = `_7dra`) %>% 
  rename_at(vars(deaths:tests_per_million),
            list(~ paste0(., '_7dra')))
  
cov_us <- cov_us %>% 
  left_join(df, by = c('st', 'dt'))

ck <- cov_us %>% filter(!is.na(tests))
assertthat::assert_that(all(ck$pos + ck$neg == ck$tests))


# pop_ga <- pop_us %>%
#   filter(st == 'GA') %>% 
#   .$pop_est


# ## dates GA schools closed ##
# 
# ga_sch_closed <- tribble(
#   ~from,         ~to,
#   "2020-03-18", NA
# )


```



Testing
=======================================================================

Row
-----------------------------------------------------------------------

### Total Tests/Percent of Population Tested

```{r}

df <- cov_us %>% 
  select(st, pop_est, dt, tests) %>% 
  arrange(st, dt) %>% 
  group_by(st) %>% 
  filter(row_number() == n()) %>% 
  ungroup() %>% 
  mutate(not_tested = pop_est - tests,
         pct_tested = tests/pop_est*100) %>%
  mutate(rank = min_rank(desc(pct_tested))) %>%  
  filter(st == "GA") %>% 
  pivot_longer(
    cols = -c(st, dt, pct_tested, pop_est, rank),
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  mutate(lab = case_when(pct_tested < 1 & var == 'tests' ~ 
                           glue('<1% of Georgians have been tested
                           for COVID-19
                           ({format(val, trim = TRUE, big.mark = ",")} out of {format(pop_est, big.mark = ",")})
                           
Testing Percentage Rank =  {rank} of 51'),
                         pct_tested >= 1 & var == 'tests' ~ 
                           glue('{pct_tested}% of Georgians have been tested
                           for COVID-19
                           ({format(val, trim = TRUE, big.mark = ",")} out of {format(pop_est, big.mark = ",")})
                           
Testing Percentage Rank = {rank} of 51'),
                         TRUE ~ '')) %>% 
  mutate(fraction = val/sum(val),
         ymax = cumsum(fraction),
         ymin = lag(ymax, default = 0),
         lab_position = (ymin + ymax)/2) 


# donut chart
library(ggrepel)

gg <- ggplot(df, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=var)) +
  geom_rect() +
  #geom_text(x=2, aes(y=lab_position, label=lab, color=var), size=4) + # x here controls label position (inner / outer)
  geom_text_repel(x = 3.5, aes(y = lab_position, label = lab),
                  nudge_x = -3.75,
                  nudge_y = 0.03) +
                  #direction    = "x",
                  #vjust        = 1.0) +
                  #segment.size = 0.2) +
  scale_fill_brewer(palette= "Greys", direction = 1) +
  scale_color_brewer(palette="Greys", direction = 1) +
  coord_polar(theta="y") +
  xlim(c(-1, 4)) +
  theme_void() +
  theme(legend.position = "none")

gg


```

> Sources: [The COVID Tracking Project](https://covidtracking.com/api/), [U.S. Census Bureau](https://www.census.gov/data/tables/time-series/demo/popest/2010s-state-total.html#par_textimage)


### Tests Per Million Residents (7-day rolling average)
Georgia is shown in <span style="color: dodgerblue;">blue</span>, compared to trends for other states, shown in <span style="color: grey90;">grey</span>.

```{r}

df <- cov_us %>% 
  filter(!is.na(tests_per_million_7dra)) %>% 
  mutate(st = as.character(st)) %>% 
  select(st, dt, tests_per_million_7dra) %>% 
  mutate(val = tests_per_million_7dra)

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = st, group = factor(st))) +
  geom_line(data = df %>% filter(st != "GA"), color = "grey90") +
  geom_line(data = df %>% filter(st == "GA"), color = "dodgerblue") +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  ylab("Tests per Million Residents") +
  xlab("Date") +
  theme_minimal()

ggplotly(gg,
         tooltip = c("st", "dt", "val"))

```

> Sources: [The COVID Tracking Project](https://covidtracking.com/api/), [U.S. Census Bureau](https://www.census.gov/data/tables/time-series/demo/popest/2010s-state-total.html#par_textimage)

Row
-----------------------------------------------------------------------

### Test Positive Rate (7-day rolling average)
Georgia is shown in <span style="color: dodgerblue;">blue</span>, compared to trends for other states, shown in <span style="color: grey90;">grey</span>.

```{r}

df <- cov_us %>%
  #exclude missing data
  filter(!is.na(pct_pos_7dra)) %>% 
  # #limit to 100 tests per day minimum
  filter(tests >= 1000) %>% 
  # mutate(st = as.character(st)) %>% 
  select(st, dt, pop_est, tests, pct_pos_7dra) %>% 
  # full_join(pop_us,
  #           by = 'st') %>% 
  # filter(!is.na(state)) %>% 
  rename(val = pct_pos_7dra)


gg <- ggplot(data = df,
              aes(x = dt, y = val, label = st, group = factor(st))) +
  geom_line(data = df %>% filter(st != "GA"), color = "grey90") +
  geom_line(data = df %>% filter(st == "GA"), color = "dodgerblue") +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, 100)) +
  ylab("Percent Positive") +
  xlab("Date") +
  theme_minimal()

ggplotly(gg,
         tooltip = c("st", "dt", "val"))



```

> Source: [The COVID Tracking Project](https://covidtracking.com/api/)

### Testing Growth vs Positive Cases Growth (7-day rolling average)

```{r}

df <- cov_us %>% 
  filter(st == "GA") %>% 
  filter(dt >= ymd('2020-03-18')) %>% 
  select(dt, tests, pos) %>% 
  pivot_longer(
    cols = -dt,
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-18'), 
                            glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                            glue('{format(val, big.mark = ",")}'))) %>% 
  filter(dt >= ymd('2020-03-19'))

gg <- ggplot(data = df,
              aes(x = dt, y = pct_chg, color = var, label = N)) +
  geom_point() +
  geom_line() +
  #geom_text(aes(label = gg_label), position = position_nudge(y = 100)) +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, 100)) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "label"))

```



Cases
=======================================================================

Row
-----------------------------------------------------------------------

### Daily cumulative total of positive COVID-19 cases in Georgia (since March 4th)

```{r}

df <- cov_us %>% 
  filter(st == "GA") %>% 
  select(dt, pos) %>% 
  pivot_longer(
    cols = -dt,  
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-04'), 
                     glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                     glue('{format(val, big.mark = ",")}')))

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = N)) +
  geom_bar(stat = 'identity', fill = "grey90") +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "N"))

```

> Sources: [The COVID Tracking Project](https://covidtracking.com/api/), [GA DPH](https://dph.georgia.gov/covid-19-daily-status-report)

### New positive COVID-19 cases in Georgia by date (since March 4th)

```{r}

df <- cov_us %>% 
  filter(st == "GA") %>% 
  select(dt, new_cases) %>% 
  pivot_longer(
    cols = -dt,
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-04'), 
                     glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                     glue('{format(val, big.mark = ",")}')))

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = N)) +
  geom_bar(stat = 'identity', fill = "grey90") +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "N"))

```

> Source: [The COVID Tracking Project](https://covidtracking.com/api/)



Row
-----------------------------------------------------------------------

### 7-day rolling average of cumulative total of positive COVID-19 cases in Georgia (since March 4th)

```{r}

df <- cov_us %>% 
  filter(st == "GA") %>% 
  select(dt, pos_7dra) %>% 
  pivot_longer(
    cols = -dt,  
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-04'), 
                     glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                     glue('{format(val, big.mark = ",")}')))

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = N)) +
  geom_point() +
  geom_line() +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "N"))

```

> Sources: [The COVID Tracking Project](https://covidtracking.com/api/)

### 7-day rolling average of new positive COVID-19 cases in Georgia by date (since March 4th)

```{r}

df <- cov_us %>%
  filter(st == "GA") %>% 
  select(dt, new_cases_7dra) %>% 
  pivot_longer(
    cols = -dt,
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-04'), 
                     glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                     glue('{format(val, big.mark = ",")}')))

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = N)) +
  geom_point() +
  geom_line() +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "N"))

```

> Sources: [The COVID Tracking Project](https://covidtracking.com/api/), [GA DPH](https://dph.georgia.gov/covid-19-daily-status-report)



Hospitalizations
=======================================================================

Column
-----------------------------------------------------------------------

### Total

```{r}

df <- cov_us %>% 
  filter(st == "GA") %>% 
  select(dt, hosp) %>% 
  filter(!is.na(hosp)) %>% 
  pivot_longer(
    cols = -dt,  
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-04'), 
                     glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                     glue('{format(val, big.mark = ",")}')))

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = N)) +
  geom_bar(stat = 'identity') +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "N"))

```

Column
-----------------------------------------------------------------------
### New

```{r}

df <- cov_us %>% 
  filter(st == "GA") %>% 
  filter(!is.na(hosp)) %>% 
  mutate(new = if_else(row_number() == 1,
                             hosp,
                             hosp - lag(hosp))) %>% 
  select(dt, new) %>% 
  pivot_longer(
    cols = -dt,
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-04'), 
                     glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                     glue('{format(val, big.mark = ",")}')))

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = N)) +
  geom_bar(stat = 'identity') +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "N"))

```



Deaths
=======================================================================

Column
-----------------------------------------------------------------------

### Total

```{r}

df <- cov_us %>% 
  filter(st == "GA") %>% 
  select(dt, deaths) %>% 
  pivot_longer(
    cols = -dt,  
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-04'), 
                     glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                     glue('{format(val, big.mark = ",")}')))

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = N)) +
  geom_bar(stat = 'identity') +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "N"))

```


Column
-----------------------------------------------------------------------

### New

```{r}

df <- cov_us %>%  
  filter(st == "GA") %>% 
  select(dt, new_deaths) %>% 
  pivot_longer(
    cols = -dt,
    names_to = 'var',
    values_to = 'val'
  ) %>% 
  arrange(dt) %>% 
  group_by(var) %>% 
  mutate(diff = val - lag(val),
         pct_chg = diff/lag(val)*100) %>% 
  ungroup() %>% 
  mutate(N = if_else(dt > ymd('2020-03-04'), 
                     glue('{format(val, big.mark = ",")} ({if_else(sign(diff) >= 0, "+", "-")}{round(pct_chg, 1)}%)'),
                     glue('{format(val, big.mark = ",")}')))

gg <- ggplot(data = df,
              aes(x = dt, y = val, label = N)) +
  geom_bar(stat = 'identity') +
  scale_x_date(expand = c(0, 0.5)) + 
  scale_y_continuous(limits = c(0, max(df$val))) +
  theme_minimal()

ggplotly(gg,
         tooltip = c("dt", "N"))

```


